Linear Reduction: Parsing and Interpreting Code Without Trees

### 2024-11-21 Paper/paper.tex
Fixed dockerfile
attempt to push

\title{Linear Reduction: Parsing and Interpreting Code Without Trees}
\author{Ari Feiglin\inst{1}\and Dr. Yoni Zohar\inst{1}}
\institute{University of Bar Ilan, Ramat Gan, Israel}

@@

\begin{abstract}

    In this paper we discuss an alternative method to parsing and interpreting human-readable code.
    This method utilizes an iterative approach, as opposed to a recursive tree-oriented approach found in most modern compilers and interpreters.
    We will implement our algorithm in an interpreter and compare it with an interpreter created using more classical means.

@@

We will propose a novel method for the process of interpretation, which doesn't use parse trees.
Parsing code generated by context-free grammars (CFGs) is inherently a recursive process, and thus it is not surprising that our algorithm can be altered to instead produce parse trees.

@@

\begin{enumerate}
    \item $\bN$ denotes the set of natural numbers, including $0$.
    \item $\bbN$ is defined to be $\bN\cup\set\infty$.
    \item $\bZ$ denotes the set of integer numbers.
    \item $\bbZ$ is defined to be $\bZ\cup\set{\pm\infty}$.
    \item $f\colon A\partial B$ means that $f$ is a partial function from $A$ to $B$ (i.e. $\operatorname{dom}f\subseteq A$).
    \item $\epsilon$ denotes the empty string.
    \item If $\mathcal L$ is a language (a set of strings), then $\mathcal L^\epsilon$ is equal to $\mathcal L\cup\set\epsilon$.
    \item A list is denoted by $(x_1,\dots,x_n)$.
    \item The concatenation of two lists $\ell_1$ and $\ell_2$ is denoted by $\ell_1@\ell_2$.
    \item $x::\ell$ is the list whose first element is $x$ and tail is $\ell$.
\end{enumerate}

@@

The idea of the algorithm is as follows: given a string of tokens $\mb{\sigma^1}\cdots\mb{\sigma^n}$ (for readability, tokens are written in boxes), we form rules for combining two tokens.
For example $\mb{\ttt1}$ and $\mb{\ttt+}$ can be combined together to give a token $\mb{\ttt{1,+}}$.
Then if we follow a token of the form $\mb{\ttt{x,+}}$ with a token of the form $\mb{\ttt y}$, the tokens are combined to form a token $\mb{\ttt{x+y}}$.
So for example:
\[ \mbt{1} \mbt{+} \mbt{2} \mbt{+} \mbt{3} \to \mbt{1,+} \mbt2 \mbt+ \mbt3 \to \mbt{3} \mbt+ \mbt3 \to \mbt{3,+} \mbt3 \to \mbt6 \]
But what about \ttt{1+2*3}?
We'd get
\[ \mbt1 \mbt+ \mbt2 \mbt* \mbt3 \to \mbt{1,+} \mbt2 \mbt* \mbt3 \to \mbt3 \mbt* \mbt3 \to \mbt{3,*} \mbt3 \to \mbt9 \]

So to remedy this we add the concept of \textit{priorities}: for each symbol in our alphabet $\Sigma$, we assign a priority $p\in\bbN$.
This can be thought of as a \textit{priority function} $\pi\colon\Sigma\longto\bbN$.
So if the tokens $\mb{\sigma^1}\cdots\mb{\sigma^n}$ have respective priorities $p_1,\dots,p_n$ we can form the string $\mb{\sigma^1}_{p_1}\cdots\mb{\sigma^n}_{p_n}$ (where the subscript is part of the
character).
Now, we only combine two tokens if the token of the first is at least as great as the token of the second, and then the combined token gets the lower (the second) of the two priorities.
So we can assign to tokens containing numbers a priority of $\infty$, the token \ttt+ gets a priority of $1$, and $\ttt*$ gets a priority of $2$.
Then this becomes:
\[ \mbt1_\infty \mbt+_1 \mbt2_\infty \mbt*_2 \mbt3_\infty \to \mbt{1,+}_1 \mbt2_\infty \mbt*_2 \mbt3_\infty \to \mbt{1,+}_1 \mbt{2,*}_2 \mbt3_\infty \]
This cannot be combined any further, so we need another rule: we will give the final token a priority of $0$, so this becomes:
\[ \mbt{1,+}_1 \mbt{2,*}_2 \mbt3_0 \to \mbt{1,+}_1 \mbt{6}_0 \to \mbt{7}_0 \]
which is the correct result.

We can formalize this as follows: we start with an alphabet $\Sigma$.
Define $\oS=\Sigma\times\bbN$, and we define a so-called \textit{initial $\beta$-reducer}: $\hb\colon \Sigma\times\Sigma \longto \Sigma$.
This is a function which tells us how to combine tokens together.
And we extend it to a \textit{derived $\beta$-reducer} which is a function $\beta\colon\oS^*\longto\oS^*$ as follows.

@@

Notice that we need to add extra rules, like $\beta(\mbt{x,*},\mbt{y,+})=\mbt{x*y,+}$.
This is so we can handle
\begin{multline*}
    \mbt1_\infty \mbt*_2 \mbt2_\infty \mbt+_1 \mbt3_\infty \to \mbt{1,*}_2 \mbt2_\infty \mbt+_1 \mbt3_\infty \to \mbt{1,*}_2 \mbt{2,+}_1 \mbt3_\infty \to \mbt{2,+}_1 \mbt3_\infty\\
    \to \mbt{2,+}_1 \mbt3_0 \to \mbt5_0
\end{multline*}

But this has a major issue: it can't handle things like parentheses.
So we need to come up with a second attempt.

@@

Here we will abstract away the value of each term; the value of the new term given by the initial $\beta$-reducer will be determined by an output function.
Our alphabet of types $\Sigma$, instead of having a token for every number, will just have tokens for types (number, operator, etc.).
We will also have another set $\values$, the \textit{universe of values}.

@@

Finally, our \textit{initial $\beta$-reducer} is a function ($\state$ is a set of functions $\termp\partial\expi$ which we will define later)
\[ \hb\colon\termi\times\term^\epsilon \partial \termi^\epsilon\times(\bbZ\times\bbZ\to\bbZ)\times(\values\times\values\times\state\partial\values\times\termp^*\times\state) \]
and we extend this to a \textit{derived $\beta$-reducer}, a function
\[ \beta\colon\oe^*\times\state \partial \oe^*\times\state \]
inputs in $\oe^*\times\state$ will be written as $\gen\xi[\bar s]$ for $\xi\in\oe^*$ and $\bar s\in\state$.
We define $\beta^*\gen\xi[\bar s]$ to be the value obtained by composing $\beta$ with itself of $\gen\xi[\bar s]$ until the convergence of $\xi$.
Meaning
\begin{multline*}
    \beta^* = \beta^n\gen\xi[\bar s]\\
    \hbox{where $n=\min\set{n\geq1}[{\beta^n\gen\xi[\bar s]=\gen{\xi'}[\bar s'],\beta\gen{\xi'}[\bar s']=\gen{\xi'}[\bar s'']}]$}
\end{multline*}
We define $\beta\gen\xi[\bar s]$ as follows, where $\xi=\sigma^1_{p_1}(v_1)\cdots\sigma^n_{p_n}(v_n)$.
\begin{enumerate}
    \item if $\sigma^1\in\termp$ then
    \[ \beta\gen\xi[\bar s] = \gen{s(\sigma^1)_{p_1}\sigma^2_{p_2}(v_2)\cdots\sigma^n_{p_n}(v_n)}[\bar s] \]
    \item if $\hb(\sigma^1,\epsilon)=(\tau,\rho,f)$ is defined, then compute $f(v_1,\_,s)=(u,\xi',s')$ and $\beta^*\gen{\pi\xi'}[\bar s']=\gen{\xi''}[\bar s'']$, and
    \[ \beta\gen\xi[\bar s] = \gen{\tau_{\rho(p_1,\_)}\xi''\sigma^2_{p_2}(v_2)\cdots\sigma^n_{p_n}(v_n)}[\bar s''] \]
    \item if $p_1\geq p_2$ and $\hb(\sigma^1,\sigma^2)=(\tau,\rho,f)$ is defined, then compute $f(v_1,v_2,s)=(u,\xi',s')$ and $\beta^*\gen{\pi\xi'}[\bar s']=\gen{\xi''}[\bar s'']$, and
    \[ \beta\gen\xi[\bar s] = \gen{\tau_{\rho(p_1,p_2)}\xi''\sigma^3_{p_3}(v_2)\cdots\sigma^n_{p_n}(v_n)}[\bar s''] \]
    \item otherwise compute $\beta\gen{\sigma^2_{p_2}(v_2)\cdots\sigma^n_{p_n}(v_n)}[\bar s]=\gen{\xi'}[\bar s']$ and
    \[ \beta\gen\xi[\bar s] = \gen{\sigma^1_{p_1}(v_1)\xi'}[\bar s'] \]
\end{enumerate}

@@

We will implement our algorithm in an interpreter for a toy language we dubbed ``LLang''.
We will also create an interpreter for LLang using menhir\NEEDCITE{}.
In this section we will detail the implementation of our algorithm and compare and contrast the two implementations.

@@

In this section we will show that valued reduction (\S\ref{valued-reduction}) computes arithmetical expressions correctly.
To do so, we will show that valued reduction computes expressions and gives a result equal to a na\"\i ve algorithm.

@@

As opposed to pure valued (stateless) reduction, we will adopt some conventions from stateful reduction.
Since our string is a string in $(\set{\s L,\s R}\cup\s X\cup\s S)^*$ and not $\set{\s L,\s R,\s X,\s S}^*$ (note the difference!), we must first convert the string into one admissable for
$\beta$-reduction.
To do so, we use stateful reduction and use the initial state and priority map which maps elements $\s x\in\s X$ to $\s X_\infty(\s x)$, $\s S\in\s S$ to $\s S_{\pi(\s s)}(f_{\s s})$, $\s L$ to
$\s L_\infty$, and $\s R$ to $\s R_0$.
Since our state doesn't change (our initial $\beta$-reducer will not affect the state) we can assume that our string has been mapped to its associated $\oe$-string from the start.
That is, instead of strings like \ttt{1+2}, we can assume that our input strings are of the form $\s X_\infty(1)\ \s S_1(+)\ \s X_\infty(2)$.

Secondly, we will adopt the convention of having type terms, abstract terms, etc.
Our base type will be $\Sigma=\set{\s X}$, and our atomic abstract terms $\mathcal A=\set{\s L_0,\s R_1,\s S_1}$ (printable terms are $\set{\s L,\s R}\cup\s X\cup\s S$, but as said before we assumed these
are already altered by the state).

@@

We can rewrite the grammar ${\it expr}$ with priorities as follows:
\[ {\it expr} \ccoloneqq \s X_\infty \gbar \s X_\infty\ \s S_n\ {\it expr} \gbar \s L_\infty\ {\it expr}\ \s R_0 \gbar \s L_\infty\ {\it expr}\ \s R_0\ \s S_n\ {\it expr} \]
when considering an input for $\eval$, we will of course neglect the priorities in the string.
And when considering an input for $\beta$-reduction, we will act as if each character is of the term indicated with the value in the string (i.e. $1_\infty+_12_\infty\in{\it expr}$ is
$\s X_\infty(1)\s S_1(+)\s X_\infty(2)$).

@@

In this section we will comapre the runtimes of both implementations (one using linear reduction and one using menhir\NEEDCITE{}).
A few notes beforehand:
\begin{itemize}
    \item The linear reduction implementation has more features than the menhir implementation, this should not severely impact the comparisons and we will of course not be comparing the implementations
            on code which the menhir implementation does not support.
    \item LLang supports left composition.
            Meaning code of the form \ttt{f x y} is read as \ttt{(f x) y}.
            We found no way of supporting this with menhir.
            This is because our grammar for the menhir implementation contains the following fragment:
            \[ {\it value} \ccoloneqq {\it const}\gbar{\it ident}\gbar{\it funcall},\qquad {\it funcall}\ccoloneqq{\it value}\ {\it value} \]
            So \ttt{f x y} can be parsed as \ttt{f (x y)} instead:

@@

\subsection{Conclusion}

>>>>

\title{Linear Reduction: Parsing and Interpreting Code Without Trees}
\author{Ari Feiglin\inst{1}\and Yoni Zohar\inst{1}}
\institute{Bar-Ilan University, Ramat Gan, Israel}

@@

\begin{abstract}
test
    In this paper we discuss an alternative method to parsing and interpreting human-readable code.
    This method utilizes an iterative approach, as opposed to a recursive tree-oriented approach found in most modern compilers and interpreters.
    We implement our algorithm in an interpreter and compare it with an interpreter created using more classical means.

@@

We propose a novel method for the process of interpretation, which doesn't use parse trees.
Parsing code generated by context-free grammars (CFGs) is inherently a recursive process, and thus it is not surprising that our algorithm can be altered to instead produce parse trees.

The idea of the algorithm is as follows: the input is a stream of tokens, which are indivisible characters in any language.
Given a string of tokens $\mb{\sigma^1}\cdots\mb{\sigma^n}$ (for readability, tokens are written in boxes), we form rules for combining two tokens.
For example $\mb{\ttt1}$ and $\mb{\ttt+}$ can be combined together to give a token $\mb{\ttt{1,+}}$.
Then if we follow a token of the form $\mb{\ttt{x,+}}$ with a token of the form $\mb{\ttt y}$, the tokens are combined to form a token $\mb{\ttt{x+y}}$.
So for example:
\[ \mbt{1} \mbt{+} \mbt{2} \mbt{+} \mbt{3} \to \mbt{1,+} \mbt2 \mbt+ \mbt3 \to \mbt{3} \mbt+ \mbt3 \to \mbt{3,+} \mbt3 \to \mbt6 \]
But what about \ttt{1+2*3}?
We'd get
\[ \mbt1 \mbt+ \mbt2 \mbt* \mbt3 \to \mbt{1,+} \mbt2 \mbt* \mbt3 \to \mbt3 \mbt* \mbt3 \to \mbt{3,*} \mbt3 \to \mbt9 \]

So to remedy this we add the concept of \textit{priorities}: for each token in our alphabet $\Sigma$, we assign a priority $p\in\bbN$.
This can be thought of as a \textit{priority function} $\pi\colon\Sigma\longto\bbN$.
So if the tokens $\mb{\sigma^1}\cdots\mb{\sigma^n}$ have respective priorities $p_1,\dots,p_n$ we can form the string $\mb{\sigma^1}_{p_1}\cdots\mb{\sigma^n}_{p_n}$ (where the subscript is part of the
character).
Now, we only combine two tokens if the token of the first is at least as great as the token of the second, and then the combined token gets the lower (the second) of the two priorities.
So we can assign to tokens containing numbers a priority of $\infty$, the token \ttt+ gets a priority of $1$, and $\ttt*$ gets a priority of $2$.
Then this becomes:
\[ \mbt1_\infty \mbt+_1 \mbt2_\infty \mbt*_2 \mbt3_\infty \to \mbt{1,+}_1 \mbt2_\infty \mbt*_2 \mbt3_\infty \to \mbt{1,+}_1 \mbt{2,*}_2 \mbt3_\infty \]
This cannot be combined any further, so we need another rule: we give the final token a priority of $0$, so this becomes:
\[ \mbt{1,+}_1 \mbt{2,*}_2 \mbt3_0 \to \mbt{1,+}_1 \mbt{6}_0 \to \mbt{7}_0 \]
which is the correct result.

@@

\begin{enumerate}
    \item $\bN$ denotes the set of natural numbers, including $0$.
    \item $\bbN$ is defined to be $\bN\cup\set{+\infty}$.
    \item $\bZ$ denotes the set of integer numbers.
    \item $\bbZ$ is defined to be $\bZ\cup\set{\pm\infty}$.
    \item $f\colon A\partial B$ means that $f$ is a partial function from $A$ to $B$ (i.e. $\operatorname{dom}f\subseteq A$).
    \item $\epsilon$ denotes the empty string.
    \item If $\mathcal L$ is a language (a set of strings), then $\mathcal L^\epsilon$ is equal to $\mathcal L\cup\set\epsilon$.
    \item A list is denoted by $(x_1,\dots,x_n)$.
    \item The concatenation of two lists $\ell_1$ and $\ell_2$ is denoted by $\ell_1@\ell_2$.
    \item $x::\ell$ is the list whose first element is $x$ and tail is $\ell$.
\end{enumerate}

@@

We can formalize the algorithm given in the introduction as follows: we start with an alphabet of tokens $\Sigma$.
Define $\oS=\Sigma\times\bbN$, and we define a so-called \textit{initial $\beta$-reducer}: $\hb\colon \Sigma\times\Sigma \longto \Sigma$.
This is a function which tells us how to combine tokens together.
And we extend it to a \textit{derived $\beta$-reducer} which is a function $\beta\colon\oS^*\longto\oS^*$ as follows.

@@

Notice that since in our reduction we get pairs of tokens in the form $\mbt{x,*},\mbt{y,+}$, we need to add extra rules to handle these cases.
Specifically here we have $\hb(\mbt{x,*},\mbt{y,+})=\mbt{x*y,+}$.
Namely the initial beta-reducer is the function:
\begin{enumerate}
    \item $\hb(\mbt x,\mb\circ)=\mbt{x,$\circ$}$ for an operator symbol $\circ$,
    \item $\hb(\mbt{x,$\circ$},\mbt y)=\mbt{x$\circ$y}$,
    \item $\hb(\mbt{x,$\circ$},\mbt{y,$\bullet$})=\mbt{x$\circ$y,$\bullet$}$,
    \item and any other inputs can be given an arbitrary output.
\end{enumerate}
So for example we can now handle expressions of the form
\begin{multline*}
    \mbt1_\infty \mbt*_2 \mbt2_\infty \mbt+_1 \mbt3_\infty \to \mbt{1,*}_2 \mbt2_\infty \mbt+_1 \mbt3_\infty \to \mbt{1,*}_2 \mbt{2,+}_1 \mbt3_\infty \to \mbt{2,+}_1 \mbt3_\infty\\
    \to \mbt{2,+}_1 \mbt3_0 \to \mbt5_0
\end{multline*}

But this has a major issue: it can't handle things like parentheses.
We could of course handle parentheses by changing how we assign priorities: every time we see an open parentheses we could increase
the priority of each token and then beta-reduce.
But this complicates how we allocate priorities, and does not generalize well.
Furthermore the notion introduced in the next section, partial reduction, generalizes well and is used as a basepoint in the
remainder of this paper.

@@

Here we abstract away the value of each term; the value of the new term given by the initial $\beta$-reducer will be determined by an output function.
Our alphabet of types $\Sigma$, instead of having a token for every number, will just have tokens for types (number, operator, etc.).
We also have another set $\values$, the \textit{universe of values}.

@@

Finally, our \textit{initial $\beta$-reducer} is a function ($\state$ is a set of functions $\termp\partial\expi$ which we define later)
\[ \hb\colon\termi\times\term^\epsilon \partial \termi^\epsilon\times(\bbZ\times\bbZ\to\bbZ)\times(\values\times\values\times\state\partial\values\times\termp^*\times\state) \]
and we extend this to a \textit{derived $\beta$-reducer}, a function
\[ \beta\colon\oe^*\times\state \partial \oe^*\times\state \]
inputs in $\oe^*\times\state$ will be written as $\gen\xi[\bar s]$ for $\xi\in\oe^*$ and $\bar s\in\state$.
We define $\beta^*\gen\xi[\bar s]$ to be the value obtained by composing $\beta$ with itself of $\gen\xi[\bar s]$ until the convergence of $\xi$.
Meaning
\begin{multline*}
    \beta^* = \beta^n\gen\xi[\bar s]\\
    \hbox{where $n=\min\set{n\geq1}[{\beta^n\gen\xi[\bar s]=\gen{\xi'}[\bar s'],\beta\gen{\xi'}[\bar s']=\gen{\xi'}[\bar s'']}]$}
\end{multline*}
We define $\beta\gen\xi[\bar s]$ as follows, where $\xi=\sigma^1_{p_1}(v_1)\cdots\sigma^n_{p_n}(v_n)$.
\begin{enumerate}
    \item if $\sigma^1\in\termp$ then
    \[ \beta\gen\xi[\bar s] = \gen{s(\sigma^1)_{p_1}\sigma^2_{p_2}(v_2)\cdots\sigma^n_{p_n}(v_n)}[\bar s] \]
    \item if $\hb(\sigma^1,\epsilon)=(\tau,\rho,f)$ is defined, then compute $f(v_1,\_,s)=(u,\xi',s')$ and $\beta^*\gen{\pi\xi'}[\bar s']=\gen{\xi''}[\bar s'']$, and
    \[ \beta\gen\xi[\bar s] = \gen{\tau_{\rho(p_1,\_)}\xi''\sigma^2_{p_2}(v_2)\cdots\sigma^n_{p_n}(v_n)}[\bar s''] \]
    \item if $p_1\geq p_2$ and $\hb(\sigma^1,\sigma^2)=(\tau,\rho,f)$ is defined, then compute $f(v_1,v_2,s)=(u,\xi',s')$ and $\beta^*\gen{\pi\xi'}[\bar s']=\gen{\xi''}[\bar s'']$, and
    \[ \beta\gen\xi[\bar s] = \gen{\tau_{\rho(p_1,p_2)}\xi''\sigma^3_{p_3}(v_2)\cdots\sigma^n_{p_n}(v_n)}[\bar s''] \]
    \item otherwise compute $\beta\gen{\sigma^2_{p_2}(v_2)\cdots\sigma^n_{p_n}(v_n)}[\bar s]=\gen{\xi'}[\bar s']$ and
    \[ \beta\gen\xi[\bar s] = \gen{\sigma^1_{p_1}(v_1)\xi'}[\bar s'] \]
\end{enumerate}

@@

We implement our algorithm in an interpreter for a toy language we dub ``LLang''.
We also create an interpreter for LLang using menhir\NEEDCITE{}.
In this section we detail the implementation of our algorithm and compare and contrast the two implementations.

@@

In this section we show that valued reduction (\S\ref{valued-reduction}) computes arithmetical expressions correctly.
To do so, we show that valued reduction computes expressions and gives a result equal to a na\"\i ve algorithm.

@@

As opposed to pure valued (stateless) reduction, we adopt some conventions from stateful reduction.
Since our string is a string in $(\set{\s L,\s R}\cup\s X\cup\s S)^*$ and not $\set{\s L,\s R,\s X,\s S}^*$ (note the difference!), we must first convert the string into one admissable for
$\beta$-reduction.
To do so, we use stateful reduction and use the initial state and priority map which maps elements $\s x\in\s X$ to $\s X_\infty(\s x)$, $\s S\in\s S$ to $\s S_{\pi(\s s)}(f_{\s s})$, $\s L$ to
$\s L_\infty$, and $\s R$ to $\s R_0$.
Since our state doesn't change (our initial $\beta$-reducer will not affect the state) we can assume that our string has been mapped to its associated $\oe$-string from the start.
That is, instead of strings like \ttt{1+2}, we can assume that our input strings are of the form $\s X_\infty(1)\ \s S_1(+)\ \s X_\infty(2)$.

Secondly, we adopt the convention of having type terms, abstract terms, etc.
Our base type will be $\Sigma=\set{\s X}$, and our atomic abstract terms $\mathcal A=\set{\s L_0,\s R_1,\s S_1}$ (printable terms are $\set{\s L,\s R}\cup\s X\cup\s S$, but as said before we assumed these
are already altered by the state).

@@

We can rewrite the grammar ${\it expr}$ with priorities as follows:
\[ {\it expr} \ccoloneqq \s X_\infty \gbar \s X_\infty\ \s S_n\ {\it expr} \gbar \s L_\infty\ {\it expr}\ \s R_0 \gbar \s L_\infty\ {\it expr}\ \s R_0\ \s S_n\ {\it expr} \]
when considering an input for $\eval$, we will of course neglect the priorities in the string.
And when considering an input for $\beta$-reduction, we act as if each character is of the term indicated with the value in the string (i.e. $1_\infty+_12_\infty\in{\it expr}$ is
$\s X_\infty(1)\s S_1(+)\s X_\infty(2)$).

@@

In this section we compare the runtimes of both implementations (one using linear reduction and one using menhir\NEEDCITE{}).
A few notes beforehand:
\begin{itemize}
    \item The linear reduction implementation has more features than the menhir implementation, this should not severely impact the comparisons and we will of course not be comparing the implementations
            on code which the menhir implementation does not support.
    \item LLang supports left composition.
            Meaning code of the form \ttt{f x y} is read as \ttt{(f x) y}.
            We found no way of supporting this with menhir.
            This is because our grammar for the menhir implementation contains the following fragment:
            \[ {\it value} \ccoloneqq {\it const}\gbar{\it ident}\gbar{\it funcall},\qquad {\it funcall}\ccoloneqq{\it value}\ {\it value} \]
            So \ttt{f x y} can be parsed as \ttt{f (x y)} instead:

@@

\section{Conclusion}
